Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiment set that we provide here is specifically aimed at showing that
the proposed method DAU can operate efficiently on a wide range of time
discretization, without specific tuning, while standard deep Q-learning
approaches can't. DAU is compared to DDPG in continuous action settings and to DQN in
discrete action settings.

>>>>

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiment set provided here is specifically aimed at showing that
the proposed method DAU can operate efficiently on a wide range of time
discretizations, without specific tuning, while standard deep Q-learning
approaches cannot. DAU is compared to DDPG in continuous action settings and to DQN in
discrete action settings. \TODO{(We only test off-policy
algorithms.)}
